---
title: "Assignment3"
output: pdf_document
bibliography: bibliography.bib
author: Bomi and Andoh
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(WDI)
library(ggplot2)
library(bibtex)
library(rvest)
library(dplyr)
library(xml2)
library(stringr)
```

## Research Question
Twenty years since the end of Apartheid: Did the collapse of Apartheid play a significant role in reducing racial and social inequality in South Africa? Is post-apartheid South Africa better off or worse off than during the apartheid era?

## Definition of Racial and social inequality
Before conducting the data analysis to find the answer for our research question, we begin by clarifying the definitions for racial and social inequality. While social inequality broadly refers to the existence of unequal opportunities for different social status/positions within a society, racial inequality can be seen as one of dimensions of social inequality. It thus indicates the discrimination based on race in access to socioeconomic opportunities or services. In our research study, we will specifically look into racial discrimination in terms of employment, education, and income levels. Because these three indicators within the capitalism society can be seen as fundamental yet significant estimators for the quality of human well-being, we decided to include them. In addition, we will try to identify drivers of unequal income distribution by controlling possible factors and variables such as unemployment rate and education level.

## Literature review
In order for us to bring out more in-depth analysis, we undertook background researches by examining the past studies written by various researchers. First of all, according to Leibbrandt,(see @Leibbrandt), Since the fall of Apartheid(1993~2008), overall (include all races) income inequality has increased and it was mainly caused by huge inequality within black African community in South-Africa. We chose this article as the first reference since it has been cited the most for the South-African Inequality Study. Second research literature is "One Kind of Freedom: Poverty Dynamics in Post-Apartheid South Africa,"@Carter20011987 which explores whether the legacy of apartheid in terms of inequality and human insecurity has been superseded by looking at the dynamics of post-apartheid income distribution based on the data from national household surveys. "Income and Non-income Inequality in Post-Apartheid South Africa: What are the Drivers and Possible Policy Interventions?"@Devepol identifies the drivers of the reproduction of inequality in post-apartheid South Africa and argues that there had a continuous increase in inequality, strongly indicating that South African is now the one of the most consistently unequal economy in the world. Fourth background research literature is "Poverty and Well-being in Post-Apartheid South Africa: An Overview of Data, Outcomes and Policy."@Hbhorat While this study provides an overview of poverty and well-being of South African during the first decade of post-apartheid, it argues that the first ten years after the end of Apartheid has rather displayed increase in income inequality and unemployment rates. "Crime and local inequality in South Africa"@Demombynes2005265 examines the effects of local inequality and violent crime in South Africa in the post-apartheid era and claims that racial heterogeneity is highly correlated with all types of crime. Lastly, "Poverty and Inequality Dynamics in South Africa: Post-apartheid Developments in the Light of the Long-Run Legacy" makes a claim that the bottom half of the income distribution and poverty has been dominated by these black South Africans. 


## Data Gathering based on web-scraping

Closely having studied the past researches, we found that most of researchers made opposite conclusions to ours in regard to the effects of post-apartheid on the qualiaty of life in South Africa. We therefore want to test our hypothesis in the basis of the following data analysis and compare with the past studies.

We found the data of monthly earnings among races and gender. We tried to scrape the data from the website.

```{r}
URL <- 'http://businesstech.co.za/news/wealth/131524/this-is-the-average-salary-in-south-africa-by-race-and-industry/'

RaceEarningsTable <- URL %>% read_html() %>%
                    html_nodes('#container > div.content_holder > div.content > div.post_single > div.post_content > div:nth-child(11) > table') %>%
                    html_table() %>% 
                    as.data.frame
RaceEarningsTable

URL <- 'http://businesstech.co.za/news/wealth/131524/this-is-the-average-salary-in-south-africa-by-race-and-industry/'

GenderEarningsTable <- URL %>% read_html() %>%
                    html_nodes('#container > div.content_holder > div.content > div.post_single > div.post_content > div:nth-child(13) > table') %>%
                    html_table() %>% 
                    as.data.frame
GenderEarningsTable

```

## Data Cleaning and Merging
In this section, we will try to clean the data so that they can be statistical analysed.

Firstly, we use command "summary" to investigate the structure (class of variables, number of vectors) of data frames we got in the previous section.
```{r}
summary(RaceEarningsTable)
summary(GenderEarningsTable)
```

As shown, every variables has a class of "characters" even though it represents numerical data.

The data we want to have is the mean of earnings among races and gender in 2003, 2012. 

Firstly, we make TimeVector and IndivisualVector to labeling the data.

```{r}
TimeVector <- c(2003,2012) #numerical vector
IndivisualVector <- c("Male","Female","White","Asian/Indian","Coloured","BlackAfrican") #character vector
```

Then, we try to convert character vector to numerical vector.

```{r}
male2003 <- as.numeric(gsub("([0-9]+).*$", "\\1", str_replace_all(GenderEarningsTable$X5[3], fixed(" "), "")))
is.numeric(male2003)
male2003
```
As I shown above, the character variable successfully converted to numerical variable.
Then, we make function which conduct this sequence.

```{r}
Converter <- function(x){
y <- as.numeric(gsub("([0-9]+).*$", "\\1", str_replace_all(x, fixed(" "), "")))
return(y)
}
test <- Converter(x = GenderEarningsTable$X5[3])
is.numeric(test)
test
```

Then, we can apply this function to all data.

```{r}
#definition of vector
Earnings2003 <- c(0,0,0,0,0,0)
Earnings2012 <- c(0,0,0,0,0,0)

#GenderEarnings
for(i in 3:4){
  Earnings2003[i-2] = Converter(x = GenderEarningsTable$X5[i])
  Earnings2012[i-2] = Converter(x = GenderEarningsTable$X6[i])
}
#RaceEarnings
for(i in 3:6){
  Earnings2003[i] = Converter(x = RaceEarningsTable$X5[i])
  Earnings2012[i] = Converter(x = RaceEarningsTable$X6[i])
}
Earnings2003
Earnings2012
preEarnings <- data.frame(IndivisualVector,Earnings2003, Earnings2012)
preEarnings
```

The preEarnings is messy data.

So we are going to transform it into tidy data.

```{r}
library(tidyr)
Earnings <- gather(preEarnings, time, mean, Earnings2003:Earnings2012)
Earnings
```

We suceeded to make the numerical vector showing the earnings among races and genders.

## Data Gathering by using Data-API

Then, we try to gather data from WorldBank by using Worldbank Data API.

We found the GINI index of south africa.
```{r}
gini <-WDI(country = "ZA", indicator = "SI.POV.GINI")
gini
```

We suceeded to fetch the data by using WDI.



## Conduct basic descriptive statistics
The data we gathered in previous section partialy statisticaly analysed (mean and median are already calcurated). In this section, we try to figure out the trend of inequality graphycally by using descriptive statistics.


We want to plot the data frame in earning mean vs time among each indivisual.


```{r}
jikan <- c(2003,2003,2003,2003,2003,2003,2012,2012,2012,2012,2012,2012)
plot(jikan,Earnings$mean)
```

Then, We try to plot the GINI coeficient of South Africa.



## Briefly discribing

```{r}
qplot(gini$year,gini$SI.POV.GINI)
```

## Briefly discribing

As shown in the first graph, we cannot say that the inequality is decreased. This results contradicts to our hyposition.

In the second graph, we can see that the GINI index is slightly increased during 2008~2011. This means that the oveall inequality has been increased during this period.

We need further data between 1990~2016 to reject our hypothesis. Because we need both data before and after the fall of Apartheid.

# References